Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-22 article/article.tex
Commit 2024-06-22 20:14

First, we evaluated the performance of the modelled
\(\text{GHI}_\text{ref}\) in relation to the measured GHI for different
levels of atmospheric clearness, by using in the RTM the monthly
climatological AOD and WC, less their respective standard deviations.
These values represent typical atmospheres in Thessaloniki with lower
than average load of aerosols and humidity, which are the main factors
that attenuate the GHI, excluding clouds. With this approach the
simulated \(\text{GHI}_\text{ref}\) should be generally greater than the
measured GHI when aerosols are more abundant. To compensate for this, we
defined the following threshold \(\text{E}\) to compare the measured
\(\text{GHI}\): \begin{equation}
\text{CE} : \text{E} > 15 + 1.04 \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
\end{equation} This is the criterion of our CE identification.

@@

A sub-category of the CE events that is often discussed in the relevant
literature \citep{Cordero2023, Martins2022, Yordanov2015}, are the
extreme cloud enhancement (ECE) events. These are cases of CE where the
measured intensity of the irradiance exceeds the TSI at the top of the
atmosphere. In this case the threshold EEEEEEEEEE: \begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation} where: \(\theta\) the solar zenith angle, \(E_{\odot}\)
the solar constant adjusted for the actual Sun -- Earth distance, and
\(i\) each of the one-minute observation.

@@

\caption{Example of cloud identification for 2019-07-11. The green line with blue symbols depicts the measured GHI in one minute steps. The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles. The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of the cosine of SZA.}\label{fig:example-day}
\end{figure}

>>>>

First, we evaluated the performance of the modelled
\(\text{GHI}_\text{ref}\) in relation to the measured GHI for different
levels of atmospheric clearness, by using in the RTM the monthly
climatological AOD and WC, less their respective standard deviations.
These values represent typical atmospheres in Thessaloniki with lower
than average load of aerosols and humidity, which are the main factors
that attenuate the GHI, excluding clouds. With this approach the
simulated \(\text{GHI}_\text{ref}\) should be generally greater than the
measured GHI when aerosols are more abundant. To compensate for this, we
defined the following threshold \(E\) to compare the measured
\(\text{GHI}\): \begin{equation}
\text{CE} : E > 15 + 1.04 \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
\end{equation} This is the criterion of our CE identification.

@@

A sub-category of the CE events that is often discussed in the relevant
literature \citep{Cordero2023, Martins2022, Yordanov2015}, are the
extreme cloud enhancement (ECE) events. These are cases of CE where the
measured intensity of the irradiance exceeds the TSI at the top of the
atmosphere. In this case the threshold \(E\) is given by:
\begin{equation}
\text{ECE}: E > \cos(\theta) \cdot E_{\odot} \frac{r^2_\text{m}} {r^2}
\label{eq:ECE}
\end{equation} where: \(\theta\) the solar zenith angle, \(E_{\odot}\)
the solar constant adjusted for the actual Sun -- Earth distance \(r\)
and \(r_\text{m}\) is the mean Sun -- Earth distance of
\(1.496\times10^8\,\text{km}\).

@@

\caption{Example of CE identification for 2019-07-11. The green line with blue symbols depicts the measured GHI in one minute steps. The red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles. The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of the cosine of SZA.}\label{fig:example-day}
\end{figure}
